GEE models

### 2017-07-05 doc/manuscript.Rmd
finished pls sentence in methods

While GEE accounts for the longitudinal design of the data, this approach is
limited in that it cannot analyze the inherent multivariate nature of the
composition of the NEFA fraction. Therefore, to confirm the results of the GEE
analyses in a multivariate environment (all NEFA variables in a single model),
partial least squares

>>>>

While GEE accounts for the longitudinal design of the data, this approach is
limited in that it cannot analyze the inherent multivariate nature of the
composition of the NEFA fraction. Therefore, to confirm the results of the GEE
analyses in a multivariate environment (all NEFA variables in a single model),
partial least squares (PLS) was used with the outcomes as the independent variable.
